%-------------------------
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Shubham Singh} & Email : \href{mailto:singhshu.iitk.ac.in}{singhshu@iitk.ac.in}\\
  \href{http://home.iitk.ac.in/~singhshu}{home.iitk.ac.in/~singhshu} & Mobile : +91-9794842994 \\
  \href{https://github.com/shubhsherl}{Github:shubhsherl}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology Kanpur}{}
      {Mathematics and Scientific Computing(B.S.);  CPI:9.2/10.0}{August, 2017 - Present}
    \resumeSubheading
      {J.T.Golden Jubilee School}{Allahabad(U.P.), India}
      {Class XII Board Exams[CBSE]; 94.4\%}{March, 2017}
    \resumeSubheading
      {J.T.Golden Jubilee School}{Allahabad(U.P.), India}
      {Class X Board Exams; 10CGPA}{March, 2015}
  \resumeSubHeadingListEnd
%-----------Awards&Achievements---------------
\section{Awards and Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Academic Excellence Award}{IIT, Kanpur}
      {For Exceptional performance in Freshman year.}{Jan, 2018}
    \resumeSubheading
      {JEE Advanced}{India}
      {Secured AIR 1732 in JEE Advanced 2017 amongst 1.5 million candidates}{2017}
    \resumeSubheading
      {National Science Talent Search}{HRI, India}
      {Secured $2^{nd}$ position in Mathematics.}{Jan, 2017}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Work Experience}
 \resumeSubHeadingListStart

  \resumeSubheading
     {New York Office}{IIT, Kanpur}
      {Intern, Prof.Manindra Agrawal}{May 2018 - July 2018}
      \begin{itemize}
          \item {Worked on a scalable Android app, designed in MVP(Model, View, Presenter) architecture.}
          \item {Integrated Editor in app to allow rich text editing, with different source type, create and sync data with the server, save drafts and publishing attachments.}
          \item {Created a detail fragment where user data can seen in brief, and can be redirected to to user’s page.}
          \item {Improved UI/UX of the app by implementing features associated with menus, viewpagers, card views, preference layouts etc. adhering to Google’s Material Design guidelines.}
          \item{Implemented linting and unit testing as part of development workflow.}
      \end{itemize}
%-----------Relevent Courses---------------
\section{Relevent Courses}
  \resumeSubHeadingListStart
    \resumeSubItem{MTH101}
      {Real Analysis and Calculus}
    \resumeSubItem{MTH102}
      {Linear Algebra and Ordinary Differential Equation}
    \resumeSubItem{MTH302}
      {Set Theory and Logic(**)}
    \resumeSubItem{ESO207}
      {Data Structure and Algorithm(**)}
    \resumeSubItem{ESC101}
      {Introduction to Computing(A*)}
    
    \hspace*{\fill}{(A*) Awarded an exceptional performance, (**) Ongoing Courses}  
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem {\href{https://github.com/shubhsherl/Phi-Man}{Phi-Game}}
      {Dec 2016}
      
      { A Gaming software as a School project built completely in C++03, where  user can create account and play games, earn coins and unlock other games.}\\
    \resumeSubItem
    {\href{http://www.linuxfromscratch.org/lfs/}{Linux From Scratch}}
      {Self Project}{Aug 2018}
      
      {Linux From Scratch (LFS) is a project that helps to build customized Linux System from scratch. }
    \resumeSubHeadingListEnd

%--------Position of Responsibility------------
\section{Position of Responsibilty}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Counselling Service}{}
      {ACADEMIC MENTOR to students of the Freshman year, helping and guiding them in their courses.}{Aug 2018-Present}
    \resumeSubheading
      {Web Executive}{Stamatics, IIT Kanpur}
      {Maintain the WebSite of Stamatics group, Dept. of Mathematics and Statics.}{Sept 2018-Present}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}

