%-------------------------
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\textbf{#1}{:#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Shubham Singh} & Email : \href{mailto:singhshu.iitk.ac.in}{singhshu@iitk.ac.in}\\
  \href{https://shubhsherl.github.io}{shubhsherl.github.io} & Mobile : +91-9794842994 \\
  \href{https://github.com/shubhsherl}{Github:shubhsherl}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Kanpur}{Kanpur, India}
      {Mathematics and Scientific Computing(B.S.);  CPI:8.96/10.0}{July, 2017 - Present}
    \resumeSubheading
      {J.T.Golden Jubilee School}{Allahabad, India}
      {Central Board of Secondary Education, Class XII; 94.4\%}{March, 2017}
    \resumeSubheading
      {J.T.Golden Jubilee School}{Allahabad, India}
      {Central Board of Secondary Education, Class X; 10 CGPA}{March, 2015}
  \resumeSubHeadingListEnd
%-----------Awards&Achievements---------------
\section{Awards and Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Academic Excellence Award}{IIT, Kanpur}
      {For Exceptional performance in Freshman year.}{Jan, 2018}
    \resumeSubheading
      {JEE Advanced}{India}
      {Secured AIR 1732 in JEE Advanced 2017 amongst 200,000 candidates}{2017}
    \resumeSubheading
      {Science Talent Search}{\href{https://www.hri.res.in}{HRI}, Allahabad, India}
      {Secured $2^{nd}$ position in Mathematics.}{Nov, 2016}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Work Experience}
 \resumeSubHeadingListStart
\resumeSubheading
     {\href{https://leena.ai}{Leena AI}}{Gurgaon, India}
      {Intern, App Developer}{Dec 2018}
      \begin{itemize}
          \item {Worked on a scalable cross-platform app, built using React Native framework.}\vspace{-2pt}
          \item {Built a Chat app from scratch where user can chat with multiple bots assisting them with their HR, IT, and other employee related queries.}\vspace{-2pt}
          \item {Integrated web-socket in the app for two-way communication between client and server.}\vspace{-2pt}
          \item {Added push notification in app for notifying user about the updates on his/her query.}\vspace{-2pt}
      \end{itemize}

  \resumeSubheading
     {New York Office}{IIT, Kanpur}
      {Intern, Under Prof.Manindra Agrawal}{May 2018 - July 2018}
      \begin{itemize}
          \item {Worked on a scalable android app, designed in MVP(Model, View, Presenter) architecture.}\vspace{-2pt}
          \item {Integrated editor in app to allow rich text editing, with different source type, create and sync data with the server, save drafts and publishing attachments.}\vspace{-2pt}
          \item {Created a detail fragment where user data can seen in brief, and can be redirected to to user’s page.}\vspace{-2pt}
          \item {Improved UI/UX of the app by implementing features associated with menus, viewpagers, card views, preference layouts etc. adhering to Google’s Material Design guidelines.}\vspace{-2pt}
          \item{Implemented linting and unit testing as part of development workflow.}
      \end{itemize}
      
    \resumeSubheading
     {Clean Coder}{IIT, Kanpur}
      {Association of Computer Activities}{Jan 2018 - Mar 2018}
      \begin{itemize}
          \item {Under Pallav Agarwal, alumnus IIT Kanpur, Google Engineer.}\vspace{-2pt}
          \item {Userspace File System written in GoLang using GO-fuse bindings that shows code files properly formatted and allows editing of those files such that the changes are reflected in the original file.}\vspace{-2pt}
      \end{itemize}
\resumeSubHeadingListEnd
%-----------Relevent Courses---------------
\section{Relevent Courses}
  \resumeSubHeadingListStart
    \hspace{\fill}{\resumeSubItem{MTH301}
      {Analysis(\textit{i})}\hspace{42pt}
    \resumeSubItem{MTH204}
      {Abstract Algebra(\textit{i})}\hspace{26pt}
    \resumeSubItem{ESO207}
      {Data Structures and Algorithms}}
    \hspace{\fill}{\resumeSubItem{MTH201}
      {Linear Algebra}\hspace{24pt}
    \resumeSubItem{MTH302}
      {Set Theory \& Logic}\hspace{26pt}
    \resumeSubItem{ESC101}
      {Introduction to Computing(A*)}}
    \resumeSubItem{CS425}
      {Computer Networks(\textit{i})}\hspace{15pt}
    \hspace*{\fill}{(A*): Exceptional Performance, (\textit{i}): In Progress}  
  \resumeSubHeadingListEnd

% %-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem {\href{https://github.com/shubhsherl/Phi-Man}{Phi-Game}}
%       {Dec 2016}
      
%       { A Gaming software as a School project built completely in C++03, where  user can create account and play games, earn coins and unlock other games.}\\
%     \resumeSubItem
%     {\href{http://www.linuxfromscratch.org/lfs/}{Linux From Scratch}}
%       {Self Project}{Aug 2018}
      
%       {Linux From Scratch (LFS) is a project that helps to build customized Linux System from scratch. }
%     \resumeSubHeadingListEnd

%--------Position of Responsibility------------
\section{Position of Responsibilty}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Counselling Service}{IIT Kanpur}
      {Academic Mentor}{Aug 2018-Present}
      \begin{itemize}
          \item {Academic mentor to students of the freshman year, helping and guiding them in their courses.}\vspace{-2pt}
      \end{itemize}
%   \resumeSubHeadingListEnd
%-------------------------------------------
%--------Extra Currics------------
% \section{Extracurriculars}
%   \resumeSubHeadingListStart
\resumeSubheading
      {Stamatics}{IIT Kanpur}
      {Web Executive}{Sept 2018-Present}
      \begin{itemize}
          \item {Maintain the {\href{http://www.iitk.ac.in/math/STAMATICS/}{Website}} of Stamatics group, Dept. of Mathematics and Statistics.}\vspace{-2pt}
      \end{itemize}
  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}

