\cvsection{Work Experience}
\begin{cventries}

  \cventry
  {Articles, Rocket.chat}
  {Google Summer of Code}
  {}
  {Summer 2019}
  {
    \begin{cvitems}
      \item {Worked on two Open Source projects, Ghost(publishing platform) and Rocket.chat.}
      \item {Modified Ghost code to allow easy integration with Rocket.chat.}
      \item {Allows Rocket.Chat user to create account on Ghost with a simple redirect, and exploit all the features provided by Ghost.}
      \item {Implemented webhooks to keep both application database in sync.}
      \item {Added Ghost in Rocket.chat as a social feature for Rocket.chat users.}
    \end{cvitems}
  }
  
    \cventry
  {Dynamic Verifiable Frequency Based Billing, Under Prof. Sandeep Shukla}
  {C3i Center, IIT Kanpur}
  {Kanpur, India}
  {May. 2019 - July. 2019}
  {
    \begin{cvitems}
          \item {Implemented a frequency based pricing system for two-way distribution model between consumers and distributors.}
          \item {Implemented a private blockchain network using hyperledger fabric framework.}
          \item {Created a react based web application to simulate a day events in network.}
          \item {Worked on hyperledger explorer to monitor the changes in the network.}
    \end{cvitems}
  }
  
    \cventry
  {Intern, App Developer}
  {Leena AI}
  {Gurgaon, India}
  {Dec. 2018}
  {
    \begin{cvitems}
          \item {Worked on a scalable cross-platform application, built using React Native framework.}
          \item {Built a Chat app from scratch where user can chat with multiple bots assisting them with their HR, IT, and other employee related queries.}
          \item {Integrated web-socket in the app for two-way communication between client and server.}
          \item {Added push notification service in app for notifying user about the updates on his/her query.}
    \end{cvitems}
  }

  \cventry
  {Intern, under Prof. Manindra Agarwal}
  {New York Office, IIT Kanpur}
  {Kanpur, India}
  {May. 2018 - July. 2018}
  {
    \begin{cvitems}
          \item {Worked on a scalable android application, designed in MVP architecture.}
          \item {Integrated editor in app to allow rich text editing, in different source type- Markdown, HTML and WYSIWYG.}
          \item {Created a detail fragment where user data can seen in brief, and can be redirected to user’s profile.}
          \item {Improved UI/UX of the app by implementing features associated with menus, viewpagers, card views, preference layouts etc. adhering to Google’s Material Design guidelines.}
          \item{Implemented linting and unit testing as part of development workflow.}
    \end{cvitems}
  }

\end{cventries}